---
output: html_document
---

\scriptsize
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}

# Publications 

```{r, results = "asis", echo = FALSE, message = FALSE, eval = TRUE}
format.authors <- function(scholar.profile, author.name) {
  library(dplyr)

  swap_initials <- function(author.name) {
    sub("(.*) (.*)", "\\2, \\1.", trimws(author.name))
  }

  pubs <- scholar::get_publications(scholar.profile)
  pubs %>% 
    strsplit(x = .$author, split = ",") -> pubs2
  lapply(pubs2, function(x) {
    x <- swap_initials(x)
    x[length(x)] <- paste0("& ", x[length(x)])
    x <- paste0(x, collapse = ", ")
    ifelse(startsWith(x, "& "), sub("& ", "", x), x)
    }
    ) -> pubs$author
  
  author.name2 <- swap_initials(author.name)
  
  pubs %>% 
    arrange(desc(year)) %>%
    mutate(journal = paste0("*", journal, "*"),
           Publications = paste0(author, " (", year, "). ", 
                                 title, ". ", journal, ". ", 
                                 number),
           Publications = gsub(author.name2, paste0("**", author.name2, "**"), Publications)) %>% 
    select(Publications)
}

pubs <- format.authors("-dn-gUsAAAAJ&hl=en", "A Allyn")

# cat(unlist(pubs), sep = "\\\n \\\n")

```

```{r, results = "asis"}
# print_latex(as_hux(pubs))
```

16\. Lewis, A.S.L., Rollinson, C.R., **Allyn, A.J.**., Ashander, J., Brodie, S., Brookson, CB., & ... (2023). The power of forecasts to advance ecological theory. *Methods in Ecology and Evolution*. 14 (3), 746-756

15\. Braun, C.D., Lezama-Ochoa, N., Farchadi, N., Arostegui, M.C., Alexander, M., **Allyn, A.J.**., & ... (2023). Widespread habitat loss and redistribution of marine top predators in a changing ocean. *Science Advances*. 9 (32), eadi2718

14\. Braun, C.D., Arostegui, M.C., Farchadi, N., Alexander, M., Afonso, P., **Allyn, A.J.**, & ... (2023). Building use‐inspired species distribution models: Using multiple data types to examine and improve model performance. *Ecological Applications*. 33 (6), e2893

13\. **Allyn, A.J.**., Alexander, M.A., Franklin, B.S., Massiot-Granier, F., Pershing, A.J., & ... (2020). Comparing and synthesizing quantitative distribution models and qualitative vulnerability assessments to project marine species distributions under climate change. *PLoS One*. 15 (4), e0231595

12\. Kong, S., Bai, J., Lee, J.H., Chen, D., **Allyn, A.J.**, Stuart, M., Pinsky, M., Mills, K., & ... (2020). Deep hurdle networks for zero-inflated multi-target regression: Application to multiple species abundance estimation. *arXiv preprint arXiv:*. :2010.16040

11\. Staudinger, M.D., Mills, K.E., Stamieszkin, K., Record, N.R., Hudak, C.A., **Allyn, A.J.**, & ... (2019). It’s about time: A synthesis of changing phenology in the Gulf of Maine ecosystem. *Fisheries Oceanography*. 28 (5), 532-566

10\. Schuetz, J.G., Mills, K.E., **Allyn, A.J.**., Stamieszkin, K., Bris, A.L., & Pershing, A.J. (2019). Complex patterns of temperature sensitivity, not ecological traits, dictate diverse species responses to climate change. *Ecography*. 42 (1), 111-124

9\. Le Bris, A., Mills, K.E., Wahle, R.A., Chen, Y., Alexander, M.A., **Allyn, A.J.**., & ... (2018). Climate vulnerability and resilience in the most valuable North American fishery. *Proceedings of the National Academy of Sciences*. 115 (8), 1831-1836

8\. Powers, R.A., K.D., Wiley, D.N., **Allyn, A.J.**, Welch, L., & Ronconi, R. (2017). Movements and foraging habitats of great shearwaters Puffinus gravis in the Gulf of Maine. *Marine Ecology Progress Series*. 574, 211-226

7\. **Allyn, A.J.**., McKnight, A., McGarigal, K., Griffin, C.R., Kuletz, K.J., Cushing, D.A., & ... (2015). Assessing a paired logistic regression model of presence-only data to map important habitat areas of the rare Kittlitz's Murrelet Brachyramphus brevirostris. *Marine Ornithology*. 43, 65-76

6\. McKnight, A., **Allyn, A.J.**., Duffy, D.C., & Irons, D.B. (2013). ‘Stepping stone’pattern in Pacific Arctic tern migration reveals the importance of upwelling areas. *Marine Ecology Progress Series*. 491, 253-264

5\. Kuletz, K.J., Nations, C.S., Manly, B., **Allyn, A.J.**., Irons, D.B., & McKnight, A. (2013). Brachyramphus murrelet trends and the Prince William Sound, Alaska, surveys: A response to Hodges and Kirchhoff. *Marine Ornithology*. 41, 69-71

4\. **Allyn, A.J.**., McKnight, A., McGarigal, K., Griffin, C.R., Kuletz, K.J., & Irons, D.B. (2012). Relationships among Kittlitz’s murrelet habitat use, temperature-depth profiles, and landscape features in Prince William Sound, Alaska, USA. *Marine Ecology Progress Series*. 466, 233-247

3\. **Allyn, A.J.**. (2012). Population Size, Habitat Use and Diet of Kittlitz's Murrelets in Prince William Sound, Alaska. Masters Thesis. *University of Massachusetts Amherst*. https://doi.org/10.7275/2406354

2\. McKnight, A., Irons, DB., **Allyn, A.J.**., Sullivan, KM., & Suryan, RM. (2011). Winter dispersal and activity patterns of post-breeding black-legged kittiwakes Rissa tridactyla from Prince William Sound, Alaska. *Marine Ecology Progress Series*. 442, 241-253

1\. Kuletz, K.J., Nations, C.S., Manly, B., **Allyn, A.J.**., Irons, D.B., & McKnight, A. (2011). Distribution, abundance and population trends of the Kittlitz's Murrelet Brachyramphus brevirostris in Prince William Sound, Alaska. *Marine Ornithology*. 39, 97-109