---
output: html_document
---

\scriptsize
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}

# Publications 

```{r, results = "asis", echo = FALSE, message = FALSE, eval = TRUE}
format.authors <- function(scholar.profile, author.name) {
  library(dplyr)

  swap_initials <- function(author.name) {
    sub("(.*) (.*)", "\\2, \\1.", trimws(author.name))
  }

  pubs <- scholar::get_publications(scholar.profile)
  pubs %>% 
    strsplit(x = .$author, split = ",") -> pubs2
  lapply(pubs2, function(x) {
    x <- swap_initials(x)
    x[length(x)] <- paste0("& ", x[length(x)])
    x <- paste0(x, collapse = ", ")
    ifelse(startsWith(x, "& "), sub("& ", "", x), x)
    }
    ) -> pubs$author
  
  author.name2 <- swap_initials(author.name)
  
  pubs %>% 
    arrange(desc(year)) %>%
    mutate(journal = paste0("*", journal, "*"),
           Publications = paste0(author, " (", year, "). ", 
                                 title, ". ", journal, ". ", 
                                 number),
           Publications = gsub(author.name2, paste0("**", author.name2, "**"), Publications)) %>% 
    select(Publications)
}

pubs <- format.authors("-dn-gUsAAAAJ&hl=en", "A Allyn")

# cat(unlist(pubs), sep = "\\\n \\\n")

```

```{r, results = "asis"}
# print_latex(as_hux(pubs))
```

16\. Lewis, ASL., Rollinson, CR., **Allyn, A.J.**., Ashander, J., Brodie, S., Brookson, CB., & ... (2023). The power of forecasts to advance ecological theory. *Methods in Ecology and Evolution*. 14 (3), 746-756\

15\. Braun, CD., Lezama-Ochoa, N., Farchadi, N., Arostegui, MC., Alexander, M., & ... (2023). Widespread habitat loss and redistribution of marine top predators in a changing ocean. *Science Advances*. 9 (32), eadi2718\

14\. Braun, CD., Arostegui, MC., Farchadi, N., Alexander, M., Afonso, P., **Allyn, A.J.**, & ... (2023). Building use‐inspired species distribution models: Using multiple data types to examine and improve model performance. *Ecological Applications*. 33 (6), e2893\

13\. **Allyn, A.J.**., Alexander, MA., Franklin, BS., Massiot-Granier, F., Pershing, AJ., & ... (2020). Comparing and synthesizing quantitative distribution models and qualitative vulnerability assessments to project marine species distributions under climate change. *PLoS One*. 15 (4), e0231595\

12\. Kong, S., Bai, J., Lee, JH., Chen, D., **Allyn, A.J.**, Stuart, M., Pinsky, M., Mills, K., & ... (2020). Deep hurdle networks for zero-inflated multi-target regression: Application to multiple species abundance estimation. *arXiv preprint arXiv:*. :2010.16040\

11\. Staudinger, MD., Mills, KE., Stamieszkin, K., Record, NR., Hudak, CA., **Allyn, A.J.**, & ... (2019). It’s about time: A synthesis of changing phenology in the Gulf of Maine ecosystem. *Fisheries Oceanography*. 28 (5), 532-566\

10\. Schuetz, JG., Mills, KE., **Allyn, A.J.**., Stamieszkin, K., Bris, AL., & Pershing, AJ. (2019). Complex patterns of temperature sensitivity, not ecological traits, dictate diverse species responses to climate change. *Ecography*. 42 (1), 111-124\

9\. Bris, A Le., Mills, KE., Wahle, RA., Chen, Y., Alexander, MA., **Allyn, A.J.**., & ... (2018). Climate vulnerability and resilience in the most valuable North American fishery. *Proceedings of the National Academy of Sciences*. 115 (8), 1831-1836\

8\. Powers, RA., K.D., Wiley, D.N., **Allyn, A.J.**, Welch, & Ronconi, L.J. &. (2017). Movements and foraging habitats of great shearwaters Puffinus gravis in the Gulf of Maine. *Marine Ecology Progress Series*. \

7\. **Allyn, A.J.**., McKnight, A., McGarigal, K., Griffin, CR., Kuletz, KJ., Cushing, DA., & ... (2015). Assessing a paired logistic regression model of presence-only data to map important habitat areas of the rare Kittlitz's Murrelet Brachyramphus brevirostris. *Marine Ornithology*. 43, 65-76\

6\. McKnight, A., **Allyn, A.J.**., Duffy, DC., & Irons, DB. (2013). ‘Stepping stone’pattern in Pacific Arctic tern migration reveals the importance of upwelling areas. *Marine Ecology Progress Series*. 491, 253-264\

5\. Kuletz, KJ., Nations, CS., Manly, B., **Allyn, A.J.**., Irons, DB., & McKnight, A. (2013). Brachyramphus murrelet trends and the Prince William Sound, Alaska, surveys: A response to Hodges and Kirchhoff. *Marine Ornithology*. 41, 69-71\

4\. **Allyn, A.J.**., McKnight, A., McGarigal, K., Griffin, CR., Kuletz, KJ., & Irons, DB. (2012). Relationships among Kittlitz’s murrelet habitat use, temperature-depth profiles, and landscape features in Prince William Sound, Alaska, USA. *Marine Ecology Progress Series*. 466, 233-247\

3\. **Allyn, A.J.**. (2012). Population Size, Habitat Use and Diet of Kittlitz's Murrelets in Prince William Sound, Alaska. Masters Thesis. *University of Massachusetts Amherst*. https://doi.org/10.7275/2406354\

2\. McKnight, A., Irons, DB., **Allyn, A.J.**., Sullivan, KM., & Suryan, RM. (2011). Winter dispersal and activity patterns of post-breeding black-legged kittiwakes Rissa tridactyla from Prince William Sound, Alaska. *Marine Ecology Progress Series*. 442, 241-253\

1\. Kuletz, KJ., Nations, CS., Manly, B., **Allyn, A.J.**., Irons, DB., & McKnight, A. (2011). Distribution, abundance and population trends of the Kittlitz's Murrelet Brachyramphus brevirostris in Prince William Sound, Alaska. *Marine Ornithology*. 39, 97-109

# ```{r ScientificImpactFigure, echo = FALSE, fig.height=3, fig.width=10, out.width="80%", fig.align="center", eval = !short}

# source("../files/make_data_impact.R")
# plot_impact(data_scholar)
# table_impact(data_scholar, author.name = author.name, scholar.profile = scholar.profile)

# ```
